Computation and comparison of the stable northeastern United States marine boundary layer

### 2020-12-08 Paper/main.tex
Added more nomenclature

\section{Nomenclature}
{\renewcommand\arraystretch{1.0}
  \noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
ABL       & Atmospheric Boundary Layer \\
$\alpha$  & Wind shear exponent  \\
$\beta$   & Thermal expansion coefficient \\
$c_p$     & Specific heat capacity \\
$C_\epsilon$  & Turbulence model constant \\
$\Delta, \Delta_{x,y,z}$  & Grid spacing, grid spacing in x, y, z directions \\
$f$       & Frequency \\
$f_{max}$  & Maximum resolvable frequency due to mesh limits \\
$f_{Ny}$   & Nyquist frequency \\
$g, g_i$   & Gravitational acceleration \\
$h$       & Enthalpy \\
$k, TKE$  & Turbulent kinetic energy \\
$L$       & Turbulent integral length scale \\
$L_{Ob}$   & Obukhov length scale \\
$\nu_t$   & Turbulent viscosity \\
LES       & Large Eddy Simulation \\
$n_{dofs}$ & Number of degrees of freedom \\
$n_r$     & Number MPI ranks \\
$\rho$    & Density \\
$\rho_\circ$ & Reference density  \\
$\phi_h$  & Potential temperature gradient \\
$Pr_t$    & Turbulent Prandtl number \\
$R$       & Universal gas constant \\
$R_{ij}$   & Two point correlation tensor \\
SBL       & Stable Boundary Layer \\
$\theta$  & Potential temperature \\
$S_i$     & Wind spectra \\
$\sigma_i$ & Wind speed variance \\
$\tau_{ij}$ & Stress tensor \\
$TI$      & Turbulence intensity \\
$t_{ts}$  & Time per time-step \\
$\overline{U}_{horiz}$ & Time averaged horizontal velocity \\
$u_\tau$   & Friction velocity    \\
$V_1$     & Resolved wind speed at first grid level
\end{longtable*}}

>>>>

\section{Nomenclature}
{\renewcommand\arraystretch{1.0}
  \noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
ABL       & Atmospheric Boundary Layer \\
$\alpha$  & Wind shear exponent  \\
$\beta$   & Thermal expansion coefficient \\
$c_p$     & Specific heat capacity \\
$C_\epsilon$  & Turbulence model constant \\
$\Delta, \Delta_{x,y,z}$  & Grid spacing, grid spacing in x, y, z directions \\
$\epsilon_{ijk}$ & Levi-Civita symbol\\
$f$       & Frequency \\
$f_{max}$  & Maximum resolvable frequency due to mesh limits \\
$f_{Ny}$   & Nyquist frequency \\
$g, g_i$   & Gravitational acceleration \\
$h$       & Enthalpy \\
$k, TKE$  & Turbulent kinetic energy \\
$L$       & Turbulent integral length scale \\
$L_{Ob}$   & Obukhov length scale \\
$\nu_t$   & Turbulent viscosity \\
LES       & Large Eddy Simulation \\
$n_{dofs}$ & Number of degrees of freedom \\
$n_r$     & Number MPI ranks \\
$\phi_h$  & Potential temperature gradient \\
$q_j$     & Energy flux vector\\
$\rho$    & Density \\
$\rho_\circ$ & Reference density  \\
$Pr_t$    & Turbulent Prandtl number \\
$R$       & Universal gas constant \\
$R_{ij}$   & Two point correlation tensor \\
SBL       & Stable Boundary Layer \\
$S^u_i$    & ABL forcing source term \\
$S_i$     & Wind spectra \\
$\sigma_i$ & Wind speed variance \\
$\tau_{ij}$ & Stress tensor \\
$\theta$  & Potential temperature \\
$TI$      & Turbulence intensity \\
$t_{ts}$  & Time per time-step \\
$\overline{U}_{horiz}$ & Time averaged horizontal velocity \\
$u_i$     & Wind velocity in the $i$ direction  \\
$u_\tau$   & Friction velocity    \\
$V_1$     & Resolved wind speed at first grid level \\
$\Omega_i$ & Earth angular velocity vector
\end{longtable*}}

### 2020-12-08 Paper/methodology.tex
Added more nomenclature

To maintain consistency with the measured data, the turbulence
intensity (TI) is calculated using the TKE as
\begin{equation}
  \textrm{TI} =
  \frac{\sqrt{\frac{2}{3}\times\textrm{TKE}}}{\overline{U}_{horiz}} =
  \frac{\sqrt{\frac{1}{3}\left( \overline{u'_1 u'_1} + \overline{u'_2 u'_2} + \overline{u'_3 u'_3}
      \right)}}{\overline{U}_{horiz}}
\end{equation}
The averaged wind speeds were enforced at the measurement height of
20 m, and the applied wind directions were consistent with the
predominant stable direction of 225 degrees southwest.

>>>>

To maintain consistency with the measured data, the turbulence
intensity (TI) is calculated using the TKE as
\begin{equation}
  \textrm{TI} =
  \frac{\sqrt{\frac{2}{3}\times\textrm{TKE}}}{\overline{U}_{horiz}} =
  \frac{\sqrt{\frac{1}{3}\left( \overline{u'_1 u'_1} + \overline{u'_2 u'_2} + \overline{u'_3 u'_3}
      \right)}}{\overline{U}_{horiz}},
\end{equation}
where $u'_i$ is the fluctuating wind velocity in the $i$
direction. The averaged wind speeds were enforced at the measurement
height of 20 m, and the applied wind directions were consistent with
the predominant stable direction of 225 degrees southwest.

### 2020-12-08 Paper/results.tex
another sig fig edit
Added more nomenclature

In comparison, the same case for Nalu-Wind takes 3.4 s per time step which
takes a total of 75.64 hours to complete the simulation. This simulation was carried out
on 1224 MPI ranks for a grid that contains $300\times 300 \times 400$ cells. The equivalent
time per degree of freedom for Nalu-Wind is $1.1 \times 10^{-4}$ s, where degrees of freedom
are the number of nodes in the mesh. For this case AMR-Wind is more than an order of magnitude
faster per degree of freedom than Nalu-Wind. This significant speed difference is due to the use
of structured grids in AMR-Wind compared with unstructured grids in Nalu-Wind. There are many 
benefits to using structured grids and for AMR-Wind this speed advantage is mostly attributed
 to the MLMG linear solver in the AMReX library \cite{AMReX_JOSS}. This is because for each 
 time step the computational work is dominated by solving two Poisson equations (MAC projection and nodal projection).

@@

From AMR-Wind LES calculations, a number of quantities can be computed
to compare with the measured targets from Archer et al
\cite{archer2016predominance}.  In
table \ref{tab:CompareAMRallWS}, we list the TI, shear exponent
$\alpha$, friction velocity $u_\tau$, Obukhov length $L_{Ob}$,
longitudinal length scale $L$, and stability classification for each of
these three cases.  The TI values, calculated at the height $z$=20 m
fall within the target range of 4.5\% to 6.0\% for stable conditions
from the Cape Wind measurements.  The calculated friction velocities
are also similar to the values from the neutral offshore ABL
calculations of \cite{cheung2020large}, where $u_\tau$ varied from
0.15 m/s to 0.51 m/s for wind speeds of 5 m/s to 15 m/s.

>>>>

In comparison, the same case for Nalu-Wind takes 3.4 s per time step which
takes about 75 hours to complete the simulation. This simulation was carried out
on 1224 MPI ranks for a grid that contains $300\times 300 \times 400$ cells. The equivalent
time per degree of freedom for Nalu-Wind is $1.1 \times 10^{-4}$ s, where degrees of freedom
are the number of nodes in the mesh. For this case AMR-Wind is more than an order of magnitude
faster per degree of freedom than Nalu-Wind. This significant speed difference is due to the use
of structured grids in AMR-Wind compared with unstructured grids in Nalu-Wind. There are many 
benefits to using structured grids and for AMR-Wind this speed advantage is mostly attributed
 to the MLMG linear solver in the AMReX library \cite{AMReX_JOSS}. This is because for each 
 time step the computational work is dominated by solving two Poisson equations (MAC projection and nodal projection).

@@

From AMR-Wind LES calculations, a number of quantities can be computed
to compare with the measured targets from Archer et al. 
\cite{archer2016predominance}.  In
table \ref{tab:CompareAMRallWS}, we list the TI, shear exponent
$\alpha$, friction velocity $u_\tau$, Obukhov length $L_{Ob}$,
longitudinal length scale $L$, and stability classification for each of
these three cases.  The TI values, calculated at the height $z$=20 m
fall within the target range of 4.5\% to 6.0\% for stable conditions
from the Cape Wind measurements.  The calculated friction velocities
are also similar to the values from the neutral offshore ABL
calculations of \cite{cheung2020large}, where $u_\tau$ varied from
0.15 m/s to 0.51 m/s for wind speeds of 5 m/s to 15 m/s.
